%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Mobile App Developer \& Database Engineer} % Job title
    {Guy's and St. Thomas’ Hospital NHS Trust} % Organization
    {London, United Kingdom} % Location
    {Feb. --- Mar. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed a medical Doctor-Patient communication and test compliance mobile application (iOS and Android) and admin web app (Vue.js) package called \href{https://davzzar.github.io/prep-page/}{\uline{``Prep.''}} in a team of 8 as the ``Major Project'' during the 2\textsuperscript{nd} year at KCL.}
        \item {Managed and maintained a consistent Git version control history and conventions for the whole duration of the project.}
        \item {Designed and implemented several mobile application modules intended for use by patients aged c. between 40 and 60 years old focusing on accessibility, utilizing Google’s Flutter framework.}
        \item {Prototyped/Designed the UI theme and other UI elements for the mobile application with emphasis on ease of use and readability.}
        \item {Designed and implemented the back-end database structure used for the app with hard emphasis on privacy, information leak prevention, and enterprise scalability using Google’s NoSQL Firebase database.}
        \item {Created a \href{https://drive.google.com/file/d/1Pu6NSpqPXnWcaanUpIu_gd5C1bQnOyQi/preview}{\underl{screencast}} presenting the final application.}
        \item {\textbf{Solution has been shortlisted for funding.}}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
