%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Extracurricular Activity \& Volunteering}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

  %---------------------------------------------------------
  \cventry
  {Temporary Member/Active Participant} % Job Title
  {KCL Informatics Student-Staff Liaison (Unofficial)} % Organisation
  {London, United Kingdom} % Location
  {Dec. 2019} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Volunteered time to raise and discuss possible solutions to student concerns with the KCL Artificial Intelligence Planning module with both the administration of the faculty and the module leaders Dr Stefan Edelkamp \& Dr Daniele Magazzeni as a member of the student body.}
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventry
  {Insight Programme Intern} % Job Title
  {TeachFirst (Placed at Harris Academy Peckham)} % Organisation
  {Peckham, London, United Kingdom} % Location
  {Jun. 2019} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Underwent crash-course-style pedagogic training focusing on self-development in problem solving, leadership, and innovation through workshops, lectures, and practical exercises.}
      \item {Spent one week at Harris Academy Peckham serving as teaching assistant in the department of mathematics.}
      \item {Planned, prepared resources for, and delivered a mathematics lesson to a year 8 set 1 class.}
      \item {Observing teacher noted \textit{``outstanding use of pre-prepared resources, great rapport built with students, and positive and motivational attitude.''}}
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventry
  {German and Russian Language Tutor} % Job Title
  {Modern Language Center at King’s College London} % Organisation
  {London, United Kingdom} % Location
  {Apr. 2019 --- Present} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Volunteered time to run speaking practice sessions with students at the university and persons of the public.}
      \item {Evaluated and gave feedback on the students use of the language and lexicon ultimately to help students express themselves in the language.}
      \item {Helped students build confidence in speaking the language in a safe environment.}
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventry
  {Workshop Leader} % Job Title
  {Beginner's Programming and Game Development Workshop} % Organisation
  {Berlin, Germany} % Location
  {May. --- Jul. 2017} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Launched an after school beginner’s programming workshop after learning that the school did not offer adequate education in the topic `due to low demand.'}
      \item {Thought the basics of programming to a class of c. 30 students of mixed ages using Python 3 and the simple 2D game engine Game Maker Studio.}
      \item {This effort was acknowledged in the school’s yearbook that year.}
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventry
  {Competitor} % Job Title
  {ISMTF Senior Math Competition} % Organisation
  {Vienna, Austria} % Location
  {Mar. 2016} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Participated in the competition in a team of international students to further my insight into mathematics.}
      \item {Used the experience to further my communication skills and learn from representatives of foreign to me curriculums and teaching methods.}
    \end{cvitems}
  }
\end{cventries}
