%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
\cventry
{Graphics and UI/UX Designer, Frontend Developer} % Job title
{\href{https://github.com/davzzar/clim-AX}{\uline{Clim-EX: The Climate Animation Explorer}}} % Organization
{Oxford, United Kingdom} % Location
{Nov. 2019} % Date(s)
{
    \begin{cvitems}
    \bsep Submission to the \href{http://www.ox.ac.uk/students/news/2019-10-14-oxford-hack-2019}{\uline{Oxford University Hackathon 2019}}.\bsep Strived to create a project that would promote and elevate the discussion and exploration contemporary issues of climate change.\bsep Acted as the graphics designer and co-frontend developer; roles that were crucial to the project's success due to its reliance on visual appeal.\bsep Project was one of the lead contenders to the ``Hacker's Choice'' award at the hackathon.
    \end{cvitems}
}

    %---------------------------------------------------------
    \cventry
    {Designer and Programmer} % Job title
    {An Argumentation Framework Solver} % Organization
    {} % Location
    {Oct. 2019 --- Present} % Date(s)
    {
        \begin{cvitems}
            \bsep Currently designing and developing a \href{https://www.sciencedirect.com/science/article/pii/000437029400041X}{\underl{Dung's Argumentation Framework}} Solver for non-monotonic reasoning as part of my final year individual project (Bachelor's Thesis) at King's College London under the supervision of Dr Odinaldo Rodrigues.\bsep The solver is imaged to use a reduction-based approach to solving both decision and enumeration problems in all four of the original semantics presented in \href{https://www.sciencedirect.com/science/article/pii/000437029400041X}{\underl{(Dung, 1995)}}.
        \end{cvitems}
    }

    %---------------------------------------------------------
    \cventry
    {Designer and Programmer} % Job title
    {Collegiate Information Portal (KCL-info)} % Organization
    {} % Location
    {Oct. 2019 --- Present} % Date(s)
    {
        \begin{cvitems}
            \bsep Currently developing an information retrieval web API for use by staff and students of KCL. The main purpose is to provide easy access to important and up-to-date information around campus and all of its aspects in one unified place.
        \end{cvitems}
    }

    %---------------------------------------------------------
    \cventry
    {Back-end Developer} % Job title
    {KCLge Rental Catalogue Web App} % Organization
    {} % Location
    {Nov. --- Dec. 2018} % Date(s)
    {
        \begin{cvitems}
            \bsep In a team of two, developed back-end for an online-store-style web app using pure PHP and JavaScript to access an external API for game data to be cached in a MySQL database.\bsep Implemented CRUD administrative functionality including multiple account types (guest/user/admin system), game information manipulation and editing and entry, and basic rental functionality such as renting rule/restriction definition and enforcement, black-listing, and game inventory management.
        \end{cvitems}
    }
\end{cventries}

%---------------------------------------------------------
